Software Citation Principles

### 2016-03-28 sc-principles/software-citation-principles.tex
adding new member, fixing alphabetization
Reworking subsections

@@

@@

\subsection{Existing principles}

Van de Sompel et al.~\cite{VandeSompel2004} argued for registration of all units of scholarly communication, including software.\niemnote{suggesting this reference go here}
Author guidelines in F1000Research, APA authors, SSI `publish or be damned'
\cite{ssi-publish-or-be-damned} manifesto, workflow for publishing code using
GitHub and Zenodo \cite{github-citable-code-guide}.
\dmnote{There are many other journals publishing software descriptions, some even specialized in software, e.g. \href{http://www.openresearchcomputation.com}{Open Research Computation}.}

@@

Notable examples of community efforts around metadata include the AAS workshop~\cite{aas-software-index}, Project CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}, CodeMeta~\cite{codemeta}

\subsection{Studies of author motivations}

Survey of data citation practices \cite{Kratz_2015}

@@

>>>>

While not usually expressed as software citation priciples, a number of groups have developed community guidelines around software and data citation. Van de Sompel et al.~\cite{VandeSompel2004} argue for registration of all units of scholarly communication, including software. In a `Publish or be damned? An alternative impact manifesto for research software'~\cite{ssi-publish-or-be-damned}, Chue Hong lists nine principles as part of `The Research Software Impact Manifesto'.

@@

In addition, a number of academic publishers such as APA~\cite{APA-guidelines} have recommendations for submitting authors on how to cite software and journals such as F1000Research~\cite{F1000Research}, SoftwareX~\cite{softwareX}, and Open Research Computation~\cite{softwareX} allow for submissions entirely focussed on research software.

@@

@@

Notable examples of community efforts around metadata include the AAS workshop~\cite{aas-software-index}, Project CRediT~\cite{casrai-credit}, Ontosoft~\cite{ontosoft}, CodeMeta~\cite{codemeta}.

@@

Darel Finkbeiner, OSTI
